---
title: "SPHU 4160 Final"
output: html_document
---


```{r setup} 
#Preamble
#------------------------------------------------------------------------#
# Final Exam                                                             #
# Erin Goucher December 13th 2019  egoucher@tulane.edu                   #
#                                                                        #
# This is the script  for the final exam for SPHU 4160.                  #
# It was developed in R 3.5.1.                                           #
#------------------------------------------------------------------------#

library(tidyverse)
library(devtools)
library(ggplot2)
library(Hmisc)
library(knitr)
library(dplyr)

```
```{r print and get runtime}
date()
```

```{r Get Working Directory}
#getwd()
#setwd("/Users/Erin/Documents/sphu4160/fall_2019/class_library_R")
``` 

```{r Import Data}
mydata <-read.csv("nola_crime_2018.csv")

# if this is the working directory (as shown above, then it isnt a file name and wont load anything.)
```

```{r Questions 1 and 2}
dim(mydata)
```

1. 9970 observations
2. 24 variables


```{r Question 3}
unique(mydata)
#you didn't provide a response to the question, based on your table, it has 9963 rows. The correct answer is 9384 unique item numbers.
```



```{r Question 4}
distinct(mydata)
summary(mydata$Signal_Description)
```

```{r}
q4data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED ASSAULT",  select=c(Signal_Description, GNOCDC_LAB))

print(q4data)
```

```{r}
q41data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED ASSAULT (DOMESTIC)",  select=c(Signal_Description, GNOCDC_LAB))

print(q41data)
```
```{r}
q42data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED BATTERY (SHOOTING)",  select=c(Signal_Description, GNOCDC_LAB))

print(q42data)
```
```{r}
q43data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED BATTERY (CUTTING)",  select=c(Signal_Description, GNOCDC_LAB))

print(q43data)
```

```{r}
q44data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED RAPE",  select=c(Signal_Description, GNOCDC_LAB))

print(q44data)
```

```{r}
q45data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED CRIMINAL DAMAGE",  select=c(Signal_Description, GNOCDC_LAB))

print(q45data)
```

```{r}
q46data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED BATTERY",  select=c(Signal_Description, GNOCDC_LAB))

print(q46data)
```

```{r}
q47data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED BURGLARY",  select=c(Signal_Description, GNOCDC_LAB))

print(q47data)
```

```{r}
q48data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED BATTERY (DOMESTIC)",  select=c(Signal_Description, GNOCDC_LAB))

print(q48data)
```


```{r}
q49data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED BURGLARY (DOMESTIC)",  select=c(Signal_Description, GNOCDC_LAB))

print(q49data)
```


```{r}
q410data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "AGGRAVATED RAPE UNFOUNDED",  select=c(Signal_Description, GNOCDC_LAB))

print(q410data)
```


```{r}
q411data <- subset(mydata, GNOCDC_LAB == "IRISH CHANNEL" & Signal_Description == "ATTEMPTED AGGRAVATED RAPE",  select=c(Signal_Description, GNOCDC_LAB))

print(q411data)
```


4. there was only one aggravated crime in the Irish Channel

```{r Question 5}

table(mydata$GNOCDC_LAB)

#I don't see your answers to question 5 (just the table below). 
```

5.

```{r QUestion 6, 7 and 8}
popdata <- subset(mydata, select=c(pop,GNOCDC_LAB))
popdata[!duplicated(popdata[1:2]),]
sum(popdata$pop, na.rm=TRUE)
#for question 6, there are three issues: 1. I don't see that you used the dataset with only unique item numbers (n=9384). I see you using mydata which contains 9970 observations, 2. For your calculations, it should read as (no. crimes*1000)/mean(population for each neighborhood) 3. the question asks for the rate per 1000 persons for each neighborhood and not the dataset as a whole calculate the rate of crime (unique items)
```
```{r}
tulanedata <- subset(mydata, GNOCDC_LAB== "TULANE - GRAVIER", select=c(GNOCDC_LAB, pop))
print(tulanedata)
```
```{r Tulane rate of crime}
(712/17445)*1000
```

```{r Tulane ratio of crime} 
(40.81399/0.7863321)
```

```{r}
centralcitydata <- subset(mydata, GNOCDC_LAB== "CENTRAL CITY", select=c(GNOCDC_LAB, pop))
print(centralcitydata)
```
```{r Central City rate of crime}
(576/35385)*1000
```
```{r Central city ratio of crime} 
(16.27808/0.7863321)
```

```{r}
plumdata <- subset(mydata, GNOCDC_LAB== "PLUM ORCHARD", select=c(GNOCDC_LAB, pop))
print(plumdata)
```

```{r Plum Orchard rate of crime}
(98/14671)*1000
```

```{r Plum Orchard ratio of crime} 
(6.679845/0.7863321)
```

```{r}
lakeviewdata <- subset(mydata, GNOCDC_LAB== "LAKEVIEW", select=c(GNOCDC_LAB, pop))
print(lakeviewdata)
```

```{r Lakeview rate of crime}
(55/16938)*1000
```

```{r Lakeview ratio of crime} 
(3.247137/0.7863321)
```

```{r}
sevendata <- subset(mydata, GNOCDC_LAB== "SEVENTH WARD", select=c(GNOCDC_LAB, pop))
print(sevendata)
```
```{r rate of crime}
(438/23878)*1000
```

```{r ratio of crime} 
(18.34324/0.7863321)
```

```{r}
rochdata <- subset(mydata, GNOCDC_LAB== "ST. ROCH", select=c(GNOCDC_LAB, pop))
print(rochdata)
```

```{r rate of crime}
(310/32067)*1000
```

```{r ratio of crime} 
(9.667259/0.7863321)
```


```{r}
claudedata <- subset(mydata, GNOCDC_LAB== "ST. CLAUDE", select=c(GNOCDC_LAB, pop))
print(claudedata)
```

```{r rate of crime}
(316/18616)*1000
```

```{r ratio of crime} 
(16.97465/0.7863321)
```

```{r}
crossdata <- subset(mydata, GNOCDC_LAB== "HOLY CROSS", select=c(GNOCDC_LAB, pop))
print(crossdata)
```
```{r rate}
(113/12942)*1000
```

```{r ratio} 
(8.731263/0.7863321)
```


```{r}
frenchdata <- subset(mydata, GNOCDC_LAB== "FRENCH QUARTER", select=c(GNOCDC_LAB, pop))
print(frenchdata)
```
```{r rate}
(720/15172)*1000
```
```{r ratio} 
(47.45584/0.7863321)
```


```{r}
ninthdata <- subset(mydata, GNOCDC_LAB== "LOWER NINTH WARD", select=c(GNOCDC_LAB, pop))
print(ninthdata)
```


```{r rate}
(168/9228)*1000
```

```{r ratio} 
(18.20546/0.7863321)
```

```{r}
audata <- subset(mydata, GNOCDC_LAB== "AUDUBON", select=c(GNOCDC_LAB, pop))
print(audata)
```

```{r rate}
(107/37946)*1000
```

```{r ratio} 
(2.819797/0.7863321)
```

```{r}
olddata <- subset(mydata, GNOCDC_LAB== "OLD AURORA", select=c(GNOCDC_LAB, pop))
print(olddata)
```

```{r rate}
(218/40130)*1000
```

```{r ratio} 
(5.432345/0.7863321)
```

```{r}
milandata <- subset(mydata, GNOCDC_LAB== "MILAN", select=c(GNOCDC_LAB, pop))
print(milandata)
```
```{r rate}
(150/21588)*1000
```

```{r ratio} 
(6.948305/0.7863321)
```


```{r}
littledata <- subset(mydata, GNOCDC_LAB== "LITTLE WOODS", select=c(GNOCDC_LAB, pop))
print(littledata)
```

```{r rate}
(632/44947)*1000
```

```{r ratio} 
(14.06101/0.7863321)
```

```{r}
cbddata <- subset(mydata, GNOCDC_LAB== "CENTRAL BUSINESS DISTRICT", select=c(GNOCDC_LAB, pop))
print(cbddata)
```

```{r}
(582/18764)*1000
```

```{r} 
(31.01684/0.7863321)
```

```{r}
berdata <- subset(mydata, GNOCDC_LAB== "BEHRMAN", select=c(GNOCDC_LAB, pop))
print(berdata)
```
```{r}
(247/25562)*1000
```

```{r} 
(9.662781/0.7863321)
```


```{r}
leondata <- subset(mydata, GNOCDC_LAB== "LEONIDAS", select=c(GNOCDC_LAB, pop))
print(leondata)
```

```{r}
(148/21271)*1000
```

```{r} 
(6.95783/0.7863321)
```

```{r}
gendata <- subset(mydata, GNOCDC_LAB== "GENTILLY TERRACE", select=c(GNOCDC_LAB, pop))
print(gendata)
```
```{r}
(133/23183)*1000
```

```{r} 
(5.736962/0.7863321)
```



```{r}
middata <- subset(mydata, GNOCDC_LAB== "MID-CITY", select=c(GNOCDC_LAB, pop))
print(middata)
```

```{r}
(360/29937)*1000
```

```{r} 
(12.02525/0.7863321)
```

```{r}
cpdata <- subset(mydata, GNOCDC_LAB== "CITY PARK", select=c(GNOCDC_LAB, pop))
print(cpdata)
```
```{r}
(31/24140)*1000
```

```{r} 
(1.284176/0.7863321)
```


```{r}
vdldata <- subset(mydata, GNOCDC_LAB== "VILLAGE DE LEST", select=c(GNOCDC_LAB, pop))
print(vdldata)
```

```{r}
(77/25445)*1000
```

```{r} 
(3.026135/0.7863321)
```


```{r}
fischdata <- subset(mydata, GNOCDC_LAB== "FISCHER DEV", select=c(GNOCDC_LAB, pop))
print(fischdata)
```
```{r}
(27/9467)*1000
```

```{r} 
(2.852012/0.7863321)
```

```{r}
westdata <- subset(mydata, GNOCDC_LAB== "WEST RIVERSIDE", select=c(GNOCDC_LAB, pop))
print(westdata)
```

```{r}
(82/15349)*1000
```

```{r} 
(5.342368/0.7863321)
```

```{r}
tremedata <- subset(mydata, GNOCDC_LAB== "TREME - LAFITTE", select=c(GNOCDC_LAB, pop))
print(tremedata)
```

```{r}
(198/18492)*1000
```

```{r} 
(10.70733/0.7863321)
```


```{r}
talldata <- subset(mydata, GNOCDC_LAB== "TALL TIMBERS - BRECHTEL", select=c(GNOCDC_LAB, pop))
print(talldata)
```

```{r}
(229/35314)*1000
```

```{r} 
(6.48468/0.7863321)
```

```{r}
vvidata <- subset(mydata, GNOCDC_LAB== "VIAVANT - VENETIAN ISLES", select=c(GNOCDC_LAB, pop))
print(vvidata)
```

```{r}
(230/26085)*1000
```

```{r} 
(8.817328/0.7863321)
```

```{r}
lcdata <- subset(mydata, GNOCDC_LAB== "LAKE CATHERINE", select=c(GNOCDC_LAB, pop))
print(lcdata)
```
```{r}
(35/2564)*1000
```

```{r} 
(13.65055/0.7863321)
```


```{r}
dildata <- subset(mydata, GNOCDC_LAB== "DILLARD", select=c(GNOCDC_LAB, pop))
print(dildata)
```
```{r}
(125/14753)*1000
```

```{r} 
(8.472853/0.7863321)
```



```{r}
wlfdata <- subset(mydata, GNOCDC_LAB== "WEST LAKE FOREST", select=c(GNOCDC_LAB, pop))
print(wlfdata)
```

```{r}
(193/25071)*1000
```

```{r} 
(7.698137/0.7863321)
```

```{r}
hollydata <- subset(mydata, GNOCDC_LAB== "HOLLYGROVE", select=c(GNOCDC_LAB, pop))
print(hollydata)
```

```{r}
(150/11723)*1000
```

```{r} 
(12.79536/0.7863321)
```

```{r}
gertdata <- subset(mydata, GNOCDC_LAB== "GERT TOWN", select=c(GNOCDC_LAB, pop))
print(gertdata)
```
```{r}
(139/22081)*1000
```

```{r} 
(6.295005/0.7863321)
```


```{r}
ridadata <- subset(mydata, GNOCDC_LAB== "FLORIDA AREA", select=c(GNOCDC_LAB, pop))
print(ridadata)
```

```{r}
(52/9424)*1000
```

```{r} 
(5.517827/0.7863321)
```

```{r}
lcddata <- subset(mydata, GNOCDC_LAB== "LOWER GARDEN DISTRICT", select=c(GNOCDC_LAB, pop))
print(lcddata)
```
```{r}
(146/18708)*1000
```

```{r} 
(7.804148/0.7863321)
```

```{r}
bydata <- subset(mydata, GNOCDC_LAB== "BYWATER", select=c(GNOCDC_LAB, pop))
print(bydata)
```
```{r}
(155/25185)*1000
```

```{r} 
(6.154457/0.7863321)
```


```{r}
mardata <- subset(mydata, GNOCDC_LAB== "MARIGNY", select=c(GNOCDC_LAB, pop))
print(mardata)
```

```{r}
(91/11334)*1000
```

```{r} 
(8.028939/0.7863321)
```


```{r}
desiredata <- subset(mydata, GNOCDC_LAB== "DESIRE AREA", select=c(GNOCDC_LAB, pop))
print(desiredata)
```
```{r}
(181/17275)*1000
```

```{r} 
(10.47757/0.7863321)
```


```{r}
bwdata <- subset(mydata, GNOCDC_LAB== "B. W. COOPER", select=c(GNOCDC_LAB, pop))
print(bwdata)
```
```{r}
(28/7821)*1000
```

```{r} 
(3.580105/0.7863321)
```


```{r}
stddata <- subset(mydata, GNOCDC_LAB== "ST. THOMAS DEV", select=c(GNOCDC_LAB, pop))
print(stddata)
```
```{r}
(50/9002)*1000
```

```{r} 
(5.554321/0.7863321)
```


```{r}
dixdata <- subset(mydata, GNOCDC_LAB== "DIXON", select=c(GNOCDC_LAB, pop))
print(dixdata)
```

```{r}
(30/15056)*1000
```

```{r} 
(1.992561/0.7863321)
```

```{r}
navydata <- subset(mydata, GNOCDC_LAB== "U.S. NAVAL BASE", select=c(GNOCDC_LAB, pop))
print(navydata)
```
```{r}
(84/18304)*1000
```

```{r} 
(4.589161/0.7863321)
```



```{r}
pinesdata <- subset(mydata, GNOCDC_LAB== "PINES VILLAGE", select=c(GNOCDC_LAB, pop))
print(pinesdata)
```

```{r}
(134/20976)*1000
```

```{r} 
(6.388253/0.7863321)
```


```{r}
marydata <- subset(mydata, GNOCDC_LAB== "MARLYVILLE - FONTAINEBLEAU", select=c(GNOCDC_LAB, pop))
print(marydata)
```

```{r}
(82/20273)*1000
```

```{r} 
(4.044789/0.7863321)
```

```{r}
milndata <- subset(mydata, GNOCDC_LAB== "MILNEBURG", select=c(GNOCDC_LAB, pop))
print(milndata)
```

```{r}
(62/14607)*1000
```

```{r} 
(4.24454/0.7863321)
```

```{r}
rbedata <- subset(mydata, GNOCDC_LAB== "READ BLVD EAST", select=c(GNOCDC_LAB, pop))
print(rbedata)
```

```{r}
(176/21863)*1000
```

```{r} 
(8.05013/0.7863321)
```

```{r}
rbwdata <- subset(mydata, GNOCDC_LAB== "READ BLVD WEST", select=c(GNOCDC_LAB, pop))
print(rbwdata)
```
```{r}
(52/16788)*1000
```

```{r} 
(3.097451/0.7863321)
```


```{r}
algpdata <- subset(mydata, GNOCDC_LAB== "ALGIERS POINT", select=c(GNOCDC_LAB, pop))
print(algpdata)
```

```{r}
(30/12848)*1000
```

```{r} 
(2.334994/0.7863321)
```

```{r}
sbadata <- subset(mydata, GNOCDC_LAB== "ST. BERNARD AREA", select=c(GNOCDC_LAB, pop))
print(sbadata)
```


```{r}
(51/8349)*1000
```

```{r} 
(6.108516/0.7863321)
```
```{r}
tourdata <- subset(mydata, GNOCDC_LAB== "TOURO", select=c(GNOCDC_LAB, pop))
print(tourdata)
```
```{r}
(65/16244)*1000
```

```{r} 
(4.001477/0.7863321)
```


```{r}
uptdata <- subset(mydata, GNOCDC_LAB== "UPTOWN", select=c(GNOCDC_LAB, pop))
print(uptdata)
```

```{r}
(65/20018)*1000
```

```{r} 
(3.247078/0.7863321)
```

```{r}
broaddata <- subset(mydata, GNOCDC_LAB== "BROADMOOR", select=c(GNOCDC_LAB, pop))
print(broaddata)
```

```{r}
(93/15376)*1000
```

```{r} 
(6.048387/0.7863321)
```

```{r}
mcddata <- subset(mydata, GNOCDC_LAB== "McDONOGH", select=c(GNOCDC_LAB, pop))
print(mcddata)
```

```{r}
(54/7211)*1000
```

```{r} 
(7.488559/0.7863321)
```


```{r}
filmdata <- subset(mydata, GNOCDC_LAB== "FILMORE", select=c(GNOCDC_LAB, pop))
print(filmdata)
```
```{r}
(89/19005)*1000
```

```{r} 
(4.682978/0.7863321)
```


```{r}
ltodata <- subset(mydata, GNOCDC_LAB== "LAKE TERRACE & OAKS", select=c(GNOCDC_LAB, pop))
print(ltodata)
```

```{r}
(27/18362)*1000
```

```{r} 
(1.470428/0.7863321)
```

```{r}
whitdata <- subset(mydata, GNOCDC_LAB== "WHITNEY", select=c(GNOCDC_LAB, pop))
print(whitdata)
```

```{r}
(85/16136)*1000
```

```{r} 
(5.267724/0.7863321)
```

```{r}
irishdata <- subset(mydata, GNOCDC_LAB== "IRISH CHANNEL", select=c(GNOCDC_LAB, pop))
print(irishdata)
```

```{r}
(45/12852)*1000
```

```{r} 
(3.501401/0.7863321)
```


```{r}
erivdata <- subset(mydata, GNOCDC_LAB== "EAST RIVERSIDE", select=c(GNOCDC_LAB, pop))
print(erivdata)
```

```{r}
(43/8942)*1000
```

```{r} 
(4.808768/0.7863321)
```


```{r}
fairdata <- subset(mydata, GNOCDC_LAB== "FAIRGROUNDS", select=c(GNOCDC_LAB, pop))
print(fairdata)
```

```{r}
(70/16551)*1000
```

```{r} 
(4.229352/0.7863321)
```



```{r}
gentwdata <- subset(mydata, GNOCDC_LAB== "GENTILLY WOODS", select=c(GNOCDC_LAB, pop))
print(gentwdata)
```

```{r}
(21/11876)*1000
```

```{r} 
(1.768272/0.7863321)
```


```{r}
bsjdata <- subset(mydata, GNOCDC_LAB== "BAYOU ST. JOHN", select=c(GNOCDC_LAB, pop))
print(bsjdata)
```

```{r}
(50/19352)*1000
```

```{r} 
(2.583712/0.7863321)
```


```{r}
naetdata <- subset(mydata, GNOCDC_LAB== "NEW AURORA - ENGLISH TURN", select=c(GNOCDC_LAB, pop))
print(naetdata)
```

```{r}
(59/18524)*1000
```

```{r} 
(3.185057/0.7863321)
```

```{r}
fredata <- subset(mydata, GNOCDC_LAB== "FRERET", select=c(GNOCDC_LAB, pop))
print(fredata)
```

```{r}
(57/11419)*1000
```

```{r} 
(4.991681/0.7863321)
```

```{r}
gddata <- subset(mydata, GNOCDC_LAB== "GARDEN DISTRICT", select=c(GNOCDC_LAB, pop))
print(gddata)
```

```{r}
(25/11373)*1000
```

```{r} 
(2.198189/0.7863321)
```

```{r}
vistadata <- subset(mydata, GNOCDC_LAB== "LAKESHORE - LAKE VISTA", select=c(GNOCDC_LAB, pop))
print(vistadata)
```

```{r}
(16/12956)*1000
```

```{r} 
(1.234949/0.7863321)
```

```{r}
santdata <- subset(mydata, GNOCDC_LAB== "ST.  ANTHONY", select=c(GNOCDC_LAB, pop))
print(santdata)
```
```{r}
(60/13897)*1000
```

```{r} 
(4.317479/0.7863321)
```



```{r}
navadata <- subset(mydata, GNOCDC_LAB== "NAVARRE", select=c(GNOCDC_LAB, pop))
print(navadata)
```

```{r}
(17/13444)*1000
```

```{r} 
(1.264505/0.7863321)
```


```{r}
iberdata <- subset(mydata, GNOCDC_LAB== "IBERVILLE", select=c(GNOCDC_LAB, pop))
print(iberdata)
```

```{r}
(24/8858)*1000
```

```{r} 
(2.709415/0.7863321)
```

```{r}
wenddata <- subset(mydata, GNOCDC_LAB== "WEST END", select=c(GNOCDC_LAB, pop))
print(wenddata)
```

```{r}
(27/11316)*1000
```

```{r} 
(2.386002/0.7863321)
```


```{r}
ecarrolldata <- subset(mydata, GNOCDC_LAB== "EAST CARROLLTON", select=c(GNOCDC_LAB, pop))
print(ecarrolldata)
```

```{r}
(22/17782)*1000
```

```{r} 
(1.237206/0.7863321)
```

```{r}
cjsdata <- subset(mydata, GNOCDC_LAB== "BLACK PEARL", select=c(GNOCDC_LAB, pop))
print(cjsdata)
```

```{r}
(11/6569)*1000
```

```{r} 
(1.674532/0.7863321)
```

```{r}
lwooddata <- subset(mydata, GNOCDC_LAB== "LAKEWOOD", select=c(GNOCDC_LAB, pop))
print(lwooddata)
```

```{r}
(11/13989)*1000
```

```{r} 
(.7863321/0.7863321)
```



```{r}
pparkdata <- subset(mydata, GNOCDC_LAB== "PONTCHARTRAIN PARK", select=c(GNOCDC_LAB, pop))
print(pparkdata)
```

```{r}
(18/18380)*1000
```

```{r} 
(.9793254/0.7863321)
```


```{r}
flordata <- subset(mydata, GNOCDC_LAB== "FLORIDA DEV", select=c(GNOCDC_LAB, pop))
print(flordata)
```

```{r}
(6/4976)*1000
```

```{r} 
(1.205788/0.7863321)

``` 


6.	There are 9963 distinct crimes committed and 219654508 in the population, so the rate of crime is .045 per 1000 person years 

7. The neighborhoods with the largest population is Little Woods with 4494

8.	Lakewood has the lowest rate of crime with 0.7863321 per 1000 and with a population of 13989


```{r Question 9 and 10}
aggravateddata <- mydata[mydata$Signal_Description %in% c("AGGRAVATED ASSAULT", "AGGRAVATED ASSAULT (DOMESTIC)", "AGGRAVATED BATTERY (SHOOTING)", "AGGRAVATED BATTERY (CUTTING)", "AGGRAVATED RAPE", "AGGRAVATED CRIMINAL DAMAGE", "AGGRAVATED BATTERY", "AGGRAVATED BURGLARY", "AGGRAVATED BATTERY (DOMESTIC)", "AGGRAVATED BURGLARY (DOMESTIC)", "AGGRAVATED RAPE UNFOUNDED", "ATTEMPTED AGGRAVATED RAPE"), c("Signal_Description", "pop", "GNOCDC_LAB")]

print(aggravateddata)
```
```{r}
tulaneagg <- subset(aggravateddata, GNOCDC_LAB== "TULANE - GRAVIER", select=c(GNOCDC_LAB, pop))
print(tulaneagg)
```
```{r Tulane}
(4/356)
```
```{r} 
(0.01123596/0.05898876)
#the correct answer for this is: rate: 11.7512181	population: 17445	rate ratio: 16.438779
```

```{r}
centralcityagg <- subset(aggravateddata, GNOCDC_LAB== "CENTRAL CITY", select=c(GNOCDC_LAB, pop))
print(centralcityagg)
```
```{r}
(14/356)
```
```{r} 
(.03932584/0.05898876)
```

```{r}
plumagg <- subset(aggravateddata, GNOCDC_LAB== "PLUM ORCHARD", select=c(GNOCDC_LAB, pop))
print(plumagg)
```
```{r}
(13/356)
```
```{r} 
(.03651685/0.05898876)
```

```{r}
lakeviewagg <- subset(aggravateddata, GNOCDC_LAB== "LAKEVIEW", select=c(GNOCDC_LAB, pop))
print(lakeviewagg)
```
```{r}
(1/356)
```
```{r} 
(.002808989/0.05898876)
```


```{r}
sevenagg <- subset(aggravateddata, GNOCDC_LAB== "SEVENTH WARD", select=c(GNOCDC_LAB, pop))
print(sevenagg)
```
```{r}
(24/356)
```
```{r} 
(.06741573/0.05898876)
```


```{r}
rochagg <- subset(aggravateddata, GNOCDC_LAB== "ST. ROCH", select=c(GNOCDC_LAB, pop))
print(rochagg)
```
```{r}
(17/356)
```
```{r} 
(.04775281/0.05898876)
```


```{r}
claudeagg <- subset(aggravateddata, GNOCDC_LAB== "ST. CLAUDE", select=c(GNOCDC_LAB, pop))
print(claudeagg)
```
```{r}
(16/356)
```
```{r} 
(.04494382/0.05898876)
```

```{r}
crossagg <- subset(aggravateddata, GNOCDC_LAB== "HOLY CROSS", select=c(GNOCDC_LAB, pop))
print(crossagg)
```
```{r}
(5/356)
```
```{r} 
(.01404494/0.05898876)
```


```{r}
frenchagg <- subset(aggravateddata, GNOCDC_LAB== "FRENCH QUARTER", select=c(GNOCDC_LAB, pop))
print(frenchagg)
```
```{r}
(21/356)
```
```{r} 
(0.05898876/0.05898876)
```

```{r}
ninthagg <- subset(aggravateddata, GNOCDC_LAB== "LOWER NINTH WARD", select=c(GNOCDC_LAB, pop))
print(ninthagg)
```
```{r}
(6/356)
```
```{r} 
(.01685393/0.05898876)
```


```{r}
auagg <- subset(aggravateddata, GNOCDC_LAB== "AUDUBON", select=c(GNOCDC_LAB, pop))
print(auagg)
```
```{r}
(0/356)
```
```{r} 
(0/0.05898876)
```

```{r}
oldagg <- subset(aggravateddata, GNOCDC_LAB== "OLD AURORA", select=c(GNOCDC_LAB, pop))
print(oldagg)
```
```{r}
(3/356)
```
```{r} 
(.008426966/0.05898876)
```

```{r}
milanagg <- subset(aggravateddata, GNOCDC_LAB== "MILAN", select=c(GNOCDC_LAB, pop))
print(milanagg)
```
```{r}
(10/356)
```
```{r} 
(.02808989/0.05898876)
```

```{r}
littleagg <- subset(aggravateddata, GNOCDC_LAB== "LITTLE WOODS", select=c(GNOCDC_LAB, pop))
print(littleagg)
```
```{r}
(41/356)
```
```{r} 
(1.1151685/0.05898876)
```


```{r}
cbdagg <- subset(aggravateddata, GNOCDC_LAB== "CENTRAL BUSINESS DISTRICT", select=c(GNOCDC_LAB, pop))
print(cbdagg)
```
```{r}
10/356
```
```{r} 
(.02808989/0.05898876)
```


```{r}
beragg <- subset(aggravateddata, GNOCDC_LAB== "BEHRMAN", select=c(GNOCDC_LAB, pop))
print(beragg)
```
```{r}
12/356
```
```{r} 
(.03370787/0.05898876)
```


```{r}
leonagg <- subset(aggravateddata, GNOCDC_LAB== "LEONIDAS", select=c(GNOCDC_LAB, pop))
print(leonagg)
```
```{r}
5/356
```
```{r} 
(.01404494/0.05898876)
```

```{r}
genagg <- subset(aggravateddata, GNOCDC_LAB== "GENTILLY TERRACE", select=c(GNOCDC_LAB, pop))
print(genagg)
```
```{r}
7/356
```
```{r} 
(.01966292/0.05898876)
```


```{r}
midagg <- subset(aggravateddata, GNOCDC_LAB== "MID-CITY", select=c(GNOCDC_LAB, pop))
print(midagg)
```
```{r}
5/356
```
```{r} 
(.01404494/0.05898876)
```




```{r}
cpagg <- subset(aggravateddata, GNOCDC_LAB== "CITY PARK", select=c(GNOCDC_LAB, pop))
print(cpagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```


```{r}
vdlagg <- subset(aggravateddata, GNOCDC_LAB== "VILLAGE DE LEST", select=c(GNOCDC_LAB, pop))
print(vdlagg)
```
```{r}
1/356
```
```{r} 
(.002808989/0.05898876)
```


```{r}
fischagg <- subset(aggravateddata, GNOCDC_LAB== "FISCHER DEV", select=c(GNOCDC_LAB, pop))
print(fischagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```


```{r}
westagg <- subset(aggravateddata, GNOCDC_LAB== "WEST RIVERSIDE", select=c(GNOCDC_LAB, pop))
print(westagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```


```{r}
tremeagg <- subset(aggravateddata, GNOCDC_LAB== "TREME - LAFITTE", select=c(GNOCDC_LAB, pop))
print(tremeagg)
```
```{r}
5/356

```
```{r} 
(.01404494/0.05898876)
```


```{r}
tallagg <- subset(aggravateddata, GNOCDC_LAB== "TALL TIMBERS - BRECHTEL", select=c(GNOCDC_LAB, pop))
print(tallagg)
```
```{r}
8/356
```
```{r} 
(.02247191/0.05898876)
```


```{r}
vviagg <- subset(aggravateddata, GNOCDC_LAB== "VIAVANT - VENETIAN ISLES", select=c(GNOCDC_LAB, pop))
print(vviagg)
```
```{r}
9/356
```
```{r} 
(.0252809/0.05898876)
```


```{r}
lcagg <- subset(aggravateddata, GNOCDC_LAB== "LAKE CATHERINE", select=c(GNOCDC_LAB, pop))
print(lcagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```


```{r}
dilagg <- subset(aggravateddata, GNOCDC_LAB== "DILLARD", select=c(GNOCDC_LAB, pop))
print(dilagg)
```
```{r}
3/356
```
```{r} 
(.008426966/0.05898876)
```


```{r}
wlfagg <- subset(aggravateddata, GNOCDC_LAB== "WEST LAKE FOREST", select=c(GNOCDC_LAB, pop))
print(wlfagg)
```
```{r}
14/356
```
```{r} 
(.03932584/0.05898876)
```


```{r}
hollyagg <- subset(aggravateddata, GNOCDC_LAB== "HOLLYGROVE", select=c(GNOCDC_LAB, pop))
print(hollyagg)
```
```{r}
9/356
```
```{r} 
(.0252809/0.05898876)
```


```{r}
gertagg <- subset(aggravateddata, GNOCDC_LAB== "GERT TOWN", select=c(GNOCDC_LAB, pop))
print(gertagg)
```
```{r}
5/356
```
```{r} 
(.01404494/0.05898876)
```

```{r}
ridaagg <- subset(aggravateddata, GNOCDC_LAB== "FLORIDA AREA", select=c(GNOCDC_LAB, pop))
print(ridaagg)
```
```{r}
2/356
```
```{r} 
(.005617978/0.05898876)
```


```{r}
lcdagg <- subset(aggravateddata, GNOCDC_LAB== "LOWER GARDEN DISTRICT", select=c(GNOCDC_LAB, pop))
print(lcdagg)
```
```{r}
3/356
```
```{r} 
(.008426966/0.05898876)
```


```{r}
byagg <- subset(aggravateddata, GNOCDC_LAB== "BYWATER", select=c(GNOCDC_LAB, pop))
print(byagg)
```
```{r}
8/356
```
```{r} 
(.02247191/0.05898876)
```

```{r}
maragg <- subset(aggravateddata, GNOCDC_LAB== "MARIGNY", select=c(GNOCDC_LAB, pop))
print(maragg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```


```{r}
desireagg <- subset(aggravateddata, GNOCDC_LAB== "DESIRE AREA", select=c(GNOCDC_LAB, pop))
print(desireagg)
```
```{r}
7/356
```
```{r} 
.01966292/0.05898876
```

```{r}
bwagg <- subset(aggravateddata, GNOCDC_LAB== "B. W. COOPER", select=c(GNOCDC_LAB, pop))
print(bwagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```



```{r}
stdagg <- subset(aggravateddata, GNOCDC_LAB== "ST. THOMAS DEV", select=c(GNOCDC_LAB, pop))
print(stdagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```



```{r}
dixagg <- subset(aggravateddata, GNOCDC_LAB== "DIXON", select=c(GNOCDC_LAB, pop))
print(dixagg)
```
```{r}
2/356
```
```{r} 
.005617978/0.05898876
```


```{r}
navyagg <- subset(aggravateddata, GNOCDC_LAB== "U.S. NAVAL BASE", select=c(GNOCDC_LAB, pop))
print(navyagg)
```
```{r}
5/356
```
```{r} 
.01404494/0.05898876
```




```{r}
pinesagg <- subset(aggravateddata, GNOCDC_LAB== "PINES VILLAGE", select=c(GNOCDC_LAB, pop))
print(pinesagg)
```
```{r}
2/356
```
```{r} 
.005617978/0.05898876
```



```{r}
maryagg <- subset(aggravateddata, GNOCDC_LAB== "MARLYVILLE - FONTAINEBLEAU", select=c(GNOCDC_LAB, pop))
print(maryagg)
```
```{r}
2/356

```
```{r} 
.005617978/0.05898876
```


```{r}
milnagg <- subset(aggravateddata, GNOCDC_LAB== "MILNEBURG", select=c(GNOCDC_LAB, pop))
print(milnagg)
```
```{r}
4/356
```
```{r} 
.01123596/0.05898876
```




```{r}
rbeagg <- subset(aggravateddata, GNOCDC_LAB== "READ BLVD EAST", select=c(GNOCDC_LAB, pop))
print(rbeagg)
```
```{r}
4/356
```
```{r} 
.01123596/0.05898876
```



```{r}
rbwagg <- subset(aggravateddata, GNOCDC_LAB== "READ BLVD WEST", select=c(GNOCDC_LAB, pop))
print(rbwagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```



```{r}
algpagg <- subset(aggravateddata, GNOCDC_LAB== "ALGIERS POINT", select=c(GNOCDC_LAB, pop))
print(algpagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```



```{r}
sbaagg <- subset(aggravateddata, GNOCDC_LAB== "ST. BERNARD AREA", select=c(GNOCDC_LAB, pop))
print(sbaagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```


```{r}
touragg <- subset(aggravateddata, GNOCDC_LAB== "TOURO", select=c(GNOCDC_LAB, pop))
print(touragg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```




```{r}
uptagg <- subset(aggravateddata, GNOCDC_LAB== "UPTOWN", select=c(GNOCDC_LAB, pop))
print(uptagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```



```{r}
broadagg <- subset(aggravateddata, GNOCDC_LAB== "BROADMOOR", select=c(GNOCDC_LAB, pop))
print(broadagg)
```
```{r}
7/356
```
```{r} 
.01966292/0.05898876
```



```{r}
mcdagg <- subset(aggravateddata, GNOCDC_LAB== "McDONOGH", select=c(GNOCDC_LAB, pop))
print(mcdagg)
```
```{r}
2/356
```
```{r} 
.005617978/0.05898876
```



```{r}
filmagg <- subset(aggravateddata, GNOCDC_LAB== "FILMORE", select=c(GNOCDC_LAB, pop))
print(filmagg)
```
```{r}
2/356
```
```{r} 
.005617978/0.05898876
```




```{r}
ltoagg <- subset(aggravateddata, GNOCDC_LAB== "LAKE TERRACE & OAKS", select=c(GNOCDC_LAB, pop))
print(ltoagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```



```{r}
whitagg <- subset(aggravateddata, GNOCDC_LAB== "WHITNEY", select=c(GNOCDC_LAB, pop))
print(whitagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```



```{r}
irishagg <- subset(aggravateddata, GNOCDC_LAB== "IRISH CHANNEL", select=c(GNOCDC_LAB, pop))
print(irishagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```




```{r}
erivagg <- subset(aggravateddata, GNOCDC_LAB== "EAST RIVERSIDE", select=c(GNOCDC_LAB, pop))
print(erivagg)
```
```{r}
2/356
```
```{r} 
.005617978/0.05898876
```




```{r}
fairagg <- subset(aggravateddata, GNOCDC_LAB== "FAIRGROUNDS", select=c(GNOCDC_LAB, pop))
print(fairagg)
```
```{r}
6/356
```
```{r} 
.01685393/0.05898876
```




```{r}
gentwagg <- subset(aggravateddata, GNOCDC_LAB== "GENTILLY WOODS", select=c(GNOCDC_LAB, pop))
print(gentwagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```



```{r}
bsjagg <- subset(aggravateddata, GNOCDC_LAB== "BAYOU ST. JOHN", select=c(GNOCDC_LAB, pop))
print(bsjagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```




```{r}
naetagg <- subset(aggravateddata, GNOCDC_LAB== "NEW AURORA - ENGLISH TURN", select=c(GNOCDC_LAB, pop))
print(naetagg)
```
```{r}
3/356
```
```{r} 
.008426966/0.05898876
```




```{r}
freagg <- subset(aggravateddata, GNOCDC_LAB== "FRERET", select=c(GNOCDC_LAB, pop))
print(freagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```




```{r}
gdagg <- subset(aggravateddata, GNOCDC_LAB== "GARDEN DISTRICT", select=c(GNOCDC_LAB, pop))
print(gdagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```



```{r}
vistaagg <- subset(aggravateddata, GNOCDC_LAB== "LAKESHORE - LAKE VISTA", select=c(GNOCDC_LAB, pop))
print(vistaagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```



```{r}
santagg <- subset(aggravateddata, GNOCDC_LAB== "ST.  ANTHONY", select=c(GNOCDC_LAB, pop))
print(santagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```





```{r}
navaagg <- subset(aggravateddata, GNOCDC_LAB== "NAVARRE", select=c(GNOCDC_LAB, pop))
print(navaagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```




```{r}
iberagg <- subset(aggravateddata, GNOCDC_LAB== "IBERVILLE", select=c(GNOCDC_LAB, pop))
print(iberagg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```



```{r}
wendagg <- subset(aggravateddata, GNOCDC_LAB== "WEST END", select=c(GNOCDC_LAB, pop))
print(wendagg)
```
```{r}
2/356
```
```{r} 
.005617978/0.05898876
```




```{r}
ecarrollagg <- subset(aggravateddata, GNOCDC_LAB== "EAST CARROLLTON", select=c(GNOCDC_LAB, pop))
print(ecarrollagg)
```
```{r}
0/356
```
```{r} 
0/356
```



```{r}
cjsagg <- subset(aggravateddata, GNOCDC_LAB== "BLACK PEARL", select=c(GNOCDC_LAB, pop))
print(cjsagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```




```{r}
lwoodagg <- subset(aggravateddata, GNOCDC_LAB== "LAKEWOOD", select=c(GNOCDC_LAB, pop))
print(lwoodagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```





```{r}
pparkagg <- subset(aggravateddata, GNOCDC_LAB== "PONTCHARTRAIN PARK", select=c(GNOCDC_LAB, pop))
print(pparkagg)
```
```{r}
0/356
```
```{r} 
0/0.05898876
```




```{r}
floragg <- subset(aggravateddata, GNOCDC_LAB== "FLORIDA DEV", select=c(GNOCDC_LAB, pop))
print(floragg)
```
```{r}
1/356
```
```{r} 
.002808989/0.05898876
```

9. See calculations above
10. See calculations above



```{r Question 11}
table(mydata$Signal_Description)
```

```{r Question 11}
table(mydata$Charge_Description)
```


11. the most common signal description is Domestic disturbance 1601,  the most common charge description is theft is 733

```{r Question 12}
abusedata <- subset(mydata, Signal_Description=="DISTURBANCE (DOMESTIC)", select=c(Signal_Description, GNOCDC_LAB, pop))


print(abusedata)
```

```{r}
abusedata$rate <- ((abusedata$Signal_Description == "DISTURBANCE (DOMESTIC)")/(abusedata$pop))

distinct(abusedata)
print(abusedata)
```

```{r}
distinct(abusedata)
q12data <- subset(abusedata, select=c("rate", "GNOCDC_LAB"))
distinct(q12data)

#your figures are slightly off, for example for central city, the correct answer is no. domestic disturbances= 73	population= 35385	rate: 2.063021e-03, and for plum orchard it is: 24 (no. domestic disturbances), population=14671	rate: 1.635880e-03
```


12. See table above

```{r Question 13}




summarydata <- subset(mydata, select=c("Victim_Age", "Signal_Description", "pop", "GNOCDC_LAB"))
distinct(summarydata)



```



```{r}
na.omit(mydata$GNOCDC_LAB)

victimage <- mydata %>% group_by(GNOCDC_LAB, Victim_Age)
percentdata <- mutate(merged, rate= ((n/pop)*1000))
#code didn't run as the merged object had not previously been created, as a results the object percentdata was not created and hindered the below step

both <-right_join(percentdata, victimage)
lm(rate~meanage, data=both)
```
13. See regression above

```{r Question 14}
```

```{r Question 15}
pdata <- rpois(10000, 4.7)

print(pdata)

hist(pdata)
```

15. See histogram above




```{r Question 16}
library(datasets)
data(iris)
summary(iris)
```




```{r}
flower <- split(iris,iris$Species)
str(flower)
res <- list()
for(n in names(flower)){   
   dat <- flower[[n]]   
   res[[n]] <- data.frame(species=n,
                          mean.sepal.length=mean(dat$Sepal.Length))
                         
}
print(res)
```

16. Setosa mean length is 5.006, Veriscolor mean length is 5.936, Virginica mean length is 6.588

```{r}
library(datasets)
data(mtcars)
summary(mtcars)
```

```{r}
plot(mtcars$mpg~mtcars$disp)
abline(lm(mtcars$mpg~mtcars$disp))
#this is fine, points taken off for not using different colors to distinguish the different cylinders
```
17. See graph above

```{r}
zscores <- c(-4.89, -1.93, -1.11, 3.94, 0.46, -3.85, -0.20, 6.04,
9.36, 7.26, 4.88, 13.45, -2.93, 6.39, -16.22, -3.24, 6.86, 11.87, 1.81, -2.54)


print(zscores)

summary(zscores)
sd(zscores)
```

```{r}
((-4.89)-(1.77))/6.878557
```
```{r}
((-1.93)-(1.77))/6.878557
```
```{r}
((-1.11)-(1.77))/6.878557
```
```{r}
((3.94)-(1.77))/6.878557
```
```{r}
((.46)-(1.77))/6.878557
```
```{r}
((-3.85)-(1.77))/6.878557
```
```{r}
((-.2)-(1.77))/6.878557
```
```{r}
((6.04)-(1.77))/6.878557
```
```{r}
((9.36)-(1.77))/6.878557
```
```{r}
((7.26)-(1.77))/6.878557
```
```{r}
((4.88)-(1.77))/6.878557
```
```{r}
((13.45)-(1.77))/6.878557
```
```{r}
((-2.93)-(1.77))/6.878557
```
```{r}
((6.39)-(1.77))/6.878557
```
```{r}
((-16.22)-(1.77))/6.878557
```
```{r}
((-3.24)-(1.77))/6.878557
```
```{r}
((-6.86)-(1.77))/6.878557
```
```{r}
((11.87)-(1.77))/6.878557
```
```{r}
((1.81)-(1.77))/6.878557
```
```{r}
((-2.54)-(1.77))/6.878557

```
18. See calculations above